---
title: 'GGW-mod2: Factor Analysis'
output:
  html_document:
    theme: flatly
    toc: yes
  pdf_document:
    toc: yes
---

# Setup

```{r workspace setup, message = F, echo = F}
# load libraries
library(devtools)
library(psych)
library(stats)
library(lavaan)
library(nonnest2)
library(nFactors)
library(langcog)
library(directlabels)
library(ggplot2)
library(knitr)
library(tidyr)
library(dplyr)
library(gridExtra)
library(robustHD)

# clear workspace
rm(list = ls(all = T))
graphics.off()
```

```{r functions, message = F, echo = F}
# make na.rm = T versions of summary functions
mean_na <- function(x) {mean(x, na.rm = T)}
ci_lower_na <- function(x) {quantile(x, 0.025, na.rm = T)}
ci_upper_na <- function(x) {quantile(x, 0.975, na.rm = T)}

# make cleanup function
cleanup <- function(datasource) {
  if(datasource %in% c("study 1", "study 2")) {
    
    # set target dataset
    if(datasource == "study 1"){d <- d_raw_study1}
    if(datasource == "study 2"){d <- d_raw_study2}
    
    # enact exclusionary criteria
    d_clean_1 <- d %>%
      mutate(finished_mod = ifelse(is.na(CATCH), 0,
                                   ifelse(finished == 1, 1,
                                          0.5))) %>%
      filter(CATCH == 1, # exclude Ps who fail catch trials 
             finished_mod != 0) %>% # exclude Ps who did not complete task
      mutate(yob_correct = as.numeric(
        ifelse(as.numeric(as.character(yob)) > 1900 & 
                 as.numeric(as.character(yob)) < 2000, 
               as.numeric(as.character(yob)), NA)), # correct formatting in yob
        age_approx = 2016 - yob_correct) %>% # calculate approximate age
      mutate(gender = factor(gender, levels = c(1, 2, 0), 
                             labels = c("m", "f", "other"))) %>%
      filter(age_approx >= 18) # exclude Ps who are younger than 18 years
    
    # recode background and demographic variables
    d_clean <- d_clean_1 %>%
      mutate( # deal with study number
        study = factor(study)) %>%
      mutate( # deal with study duration
        duration = as.numeric(difftime(strptime(end_time, "%I:%M:%S"),
                                       strptime(start_time, "%I:%M:%S"),
                                       units = "mins"))) %>%
      mutate( # deal with race
        race_asian_east = 
          factor(ifelse(is.na(race_asian_east), "", "asian_east ")),
        race_asian_south = 
          factor(ifelse(is.na(race_asian_south), "", "asian_south ")),
        race_asian_other = 
          factor(ifelse(is.na(race_asian_other), "", "asian_other ")),
        race_black = 
          factor(ifelse(is.na(race_black), "", "black ")),
        race_hispanic = 
          factor(ifelse(is.na(race_hispanic), "", "hispanic ")),
        race_middle_eastern = 
          factor(ifelse(is.na(race_middle_eastern), "", "middle_eastern ")),
        race_native_american = 
          factor(ifelse(is.na(race_native_american), "", "native_american ")),
        race_pac_islander = 
          factor(ifelse(is.na(race_pac_islander), "", "pac_islander ")),
        race_white = 
          factor(ifelse(is.na(race_white), "", "white ")),
        race_other_prefno = 
          factor(ifelse(is.na(race_other_prefno), "", "other_prefno ")),
        race_cat = paste0(race_asian_east, race_asian_south, race_asian_other,
                          race_black, race_hispanic, race_middle_eastern,
                          race_native_american, race_pac_islander, race_white,
                          race_other_prefno),
        race_cat2 = factor(sub(" +$", "", race_cat)),
        race_cat3 = factor(ifelse(grepl(" ", race_cat2) == T, "multiracial",
                                  as.character(race_cat2)))) %>%
      select(study, subid:end_time, duration, finished:gender, 
             religion_buddhism:age_approx, race_cat3) %>%
      rename(race_cat = race_cat3) %>%
      mutate( # deal with religion
        religion_buddhism = 
          factor(ifelse(is.na(religion_buddhism), "", "buddhism ")),
        religion_christianity = 
          factor(ifelse(is.na(religion_christianity), "", "christianity ")),
        religion_hinduism = 
          factor(ifelse(is.na(religion_hinduism), "", "hinduism ")),
        religion_islam = 
          factor(ifelse(is.na(religion_islam), "", "islam ")),
        religion_jainism = 
          factor(ifelse(is.na(religion_jainism), "", "jainism ")),
        religion_judaism = 
          factor(ifelse(is.na(religion_judaism), "", "judaism ")),
        religion_sikhism = 
          factor(ifelse(is.na(religion_sikhism), "", "sikhism ")),
        religion_other = 
          factor(ifelse(is.na(religion_other), "", "other ")),
        religion_none = 
          factor(ifelse(is.na(religion_none), "", "none ")),
        religion_prefno = 
          factor(ifelse(is.na(religion_prefno), "", "other_prefno ")),
        religion_cat = paste0(religion_buddhism, religion_christianity, 
                              religion_hinduism, religion_islam, 
                              religion_jainism, religion_judaism, 
                              religion_sikhism, religion_other, 
                              religion_none, religion_prefno),
        religion_cat2 = factor(sub(" +$", "", religion_cat)),
        religion_cat3 = factor(ifelse(grepl(" ", religion_cat2) == T, 
                                      "multireligious",
                                      as.character(religion_cat2)))) %>%
      select(study:gender, feedback:race_cat, religion_cat3) %>%
      rename(religion_cat = religion_cat3)
    
    # remove extraneous dfs and variables
    rm(d, d_clean_1)
  }
  
  if(datasource == "study 3") {
    
    # set target dataset
    d <- d_raw_study3
    
    # enact exclusionary criteria
    d_clean_1 <- d %>%
      mutate(finished_mod = ifelse(is.na(CATCH..characterL) | 
                                     is.na(CATCH..characterR), 0,
                                   ifelse(finished == 1, 1,
                                          0.5))) %>%
      filter(CATCH..characterL == 5, # exclude Ps who fail catch trials 
             CATCH..characterR == 5,
             finished_mod != 0) %>% # exclude Ps who did not complete task
      mutate(yob_correct = as.numeric(
        ifelse(as.numeric(as.character(yob)) > 1900 & 
                 as.numeric(as.character(yob)) < 2000, 
               as.numeric(as.character(yob)), NA)), # correct formatting in yob
        age_approx = 2016 - yob_correct) %>% # calculate approximate age
      mutate(gender = factor(gender, levels = c(1, 2, 0), 
                             labels = c("m", "f", "other"))) %>%
      filter(age_approx >= 18) # exclude Ps who are younger than 18 years
    
    # recode background and demographic variables
    d_clean_2 <- d_clean_1 %>%
      mutate( # deal with study number
        study = factor(study)) %>%
      mutate( # deal with study duration
        duration = as.numeric(difftime(strptime(end_time, "%I:%M:%S"),
                                       strptime(start_time, "%I:%M:%S"),
                                       units = "mins"))) %>%
      mutate( # deal with race
        race_asian_east = 
          factor(ifelse(is.na(race_asian_east), "", "asian_east ")),
        race_asian_south = 
          factor(ifelse(is.na(race_asian_south), "", "asian_south ")),
        race_asian_other = 
          factor(ifelse(is.na(race_asian_other), "", "asian_other ")),
        race_black = 
          factor(ifelse(is.na(race_black), "", "black ")),
        race_hispanic = 
          factor(ifelse(is.na(race_hispanic), "", "hispanic ")),
        race_middle_eastern = 
          factor(ifelse(is.na(race_middle_eastern), "", "middle_eastern ")),
        race_native_american = 
          factor(ifelse(is.na(race_native_american), "", "native_american ")),
        race_pac_islander = 
          factor(ifelse(is.na(race_pac_islander), "", "pac_islander ")),
        race_white = 
          factor(ifelse(is.na(race_white), "", "white ")),
        race_other_prefno = 
          factor(ifelse(is.na(race_other_prefno), "", "other_prefno ")),
        race_cat = paste0(race_asian_east, race_asian_south, race_asian_other,
                          race_black, race_hispanic, race_middle_eastern,
                          race_native_american, race_pac_islander, race_white,
                          race_other_prefno),
        race_cat2 = factor(sub(" +$", "", race_cat)),
        race_cat3 = factor(ifelse(grepl(" ", race_cat2) == T, "multiracial",
                                  as.character(race_cat2)))) %>%
      select(study, subid:end_time, duration, finished:gender, 
             religion_buddhism:age_approx, race_cat3) %>%
      rename(race_cat = race_cat3) %>%
      mutate( # deal with religion
        religion_buddhism = 
          factor(ifelse(is.na(religion_buddhism), "", "buddhism ")),
        religion_christianity = 
          factor(ifelse(is.na(religion_christianity), "", "christianity ")),
        religion_hinduism = 
          factor(ifelse(is.na(religion_hinduism), "", "hinduism ")),
        religion_islam = 
          factor(ifelse(is.na(religion_islam), "", "islam ")),
        religion_jainism = 
          factor(ifelse(is.na(religion_jainism), "", "jainism ")),
        religion_judaism = 
          factor(ifelse(is.na(religion_judaism), "", "judaism ")),
        religion_sikhism = 
          factor(ifelse(is.na(religion_sikhism), "", "sikhism ")),
        religion_other = 
          factor(ifelse(is.na(religion_other), "", "other ")),
        religion_none = 
          factor(ifelse(is.na(religion_none), "", "none ")),
        religion_prefno = 
          factor(ifelse(is.na(religion_prefno), "", "other_prefno ")),
        religion_cat = paste0(religion_buddhism, religion_christianity, 
                              religion_hinduism, religion_islam, 
                              religion_jainism, religion_judaism, 
                              religion_sikhism, religion_other, 
                              religion_none, religion_prefno),
        religion_cat2 = factor(sub(" +$", "", religion_cat)),
        religion_cat3 = factor(ifelse(grepl(" ", religion_cat2) == T, 
                                      "multireligious",
                                      as.character(religion_cat2)))) %>%
      select(study:gender, feedback:race_cat, religion_cat3) %>%
      rename(religion_cat = religion_cat3)
    
    # rename response variables
    d_clean_3 <- d_clean_2
    names(d_clean_3) <- gsub("get", "", names(d_clean_3))
    names(d_clean_3) <- gsub("\\.", "", names(d_clean_3))
    names(d_clean_3) <- gsub("char", "_char", names(d_clean_3))
    names(d_clean_3)[names(d_clean_3) %in% c("_characterL", "_characterR")] <- 
      c("characterL", "characterR")
    
    # recode response variables (center)
    d_clean_4 <- d_clean_3
    for(i in 11:92) {
      d_clean_4[,i] <- d_clean_4[,i] - 4 # transform from 1 to 7 --> -3 to 3
    }
    
    # recode characterL vs. characterR as beetle vs. robot
    d_clean_5_demo <- d_clean_4 %>%
      select(study:condition, yob:religion_cat)
    
    d_clean_5_characterL <- d_clean_4 %>%
      mutate(target = characterL) %>%
      select(study, subid, target, happy_characterL:CATCH_characterL)
    names(d_clean_5_characterL) <- gsub("_characterL", "", 
                                        names(d_clean_5_characterL))
    
    d_clean_5_characterR <- d_clean_4 %>%
      mutate(target = characterR) %>%
      select(study, subid, target, happy_characterR:CATCH_characterR)
    names(d_clean_5_characterR) <- gsub("_characterR", "", 
                                        names(d_clean_5_characterR))
    
    d_clean <- d_clean_5_characterL %>%
      full_join(d_clean_5_characterR) %>%
      full_join(d_clean_5_demo) %>%
      select(study, subid, date:religion_cat, target:CATCH)
    
    # remove extraneous dfs and variables
    rm(d, d_clean_1, d_clean_2, d_clean_3, d_clean_4, d_clean_5_characterL, 
       d_clean_5_characterR, d_clean_5_demo, i)
  }
  
  if(datasource == "study 4") {
    
    # set target dataset
    d <- d_raw_study4

        # enact exclusionary criteria
    d_clean_1 <- d %>%
      mutate(finished_mod = ifelse(is.na(CATCH), 0,
                                   ifelse(finished == 1, 1,
                                          0.5))) %>%
      filter(CATCH == 1, # exclude Ps who fail catch trials 
             finished_mod != 0) %>% # exclude Ps who did not complete task
      mutate(yob_correct = as.numeric(
        ifelse(as.numeric(as.character(yob)) > 1900 & 
                 as.numeric(as.character(yob)) < 2000, 
               as.numeric(as.character(yob)), NA)), # correct formatting in yob
        age_approx = 2016 - yob_correct) %>% # calculate approximate age
      mutate(gender = factor(gender, levels = c(1, 2, 0), 
                             labels = c("m", "f", "other"))) %>%
      filter(age_approx >= 18) # exclude Ps who are younger than 18 years
    
    # recode one character
    d_clean_2 <- d_clean_1 %>%
      mutate(condition = factor(ifelse(
        grepl("vegetative", as.character(condition)), "pvs",
        ifelse(grepl("blue", as.character(condition)), "bluejay",
               as.character(condition)))))
    
    # recode background and demographic variables
    d_clean <- d_clean_2 %>%
      mutate( # deal with study number
        study = factor(study)) %>%
      mutate( # deal with study duration
        duration = as.numeric(difftime(strptime(end_time, "%I:%M:%S"),
                                       strptime(start_time, "%I:%M:%S"),
                                       units = "mins"))) %>%
      mutate( # deal with race
        race_asian_east = 
          factor(ifelse(is.na(race_asian_east), "", "asian_east ")),
        race_asian_south = 
          factor(ifelse(is.na(race_asian_south), "", "asian_south ")),
        race_asian_other = 
          factor(ifelse(is.na(race_asian_other), "", "asian_other ")),
        race_black = 
          factor(ifelse(is.na(race_black), "", "black ")),
        race_hispanic = 
          factor(ifelse(is.na(race_hispanic), "", "hispanic ")),
        race_middle_eastern = 
          factor(ifelse(is.na(race_middle_eastern), "", "middle_eastern ")),
        race_native_american = 
          factor(ifelse(is.na(race_native_american), "", "native_american ")),
        race_pac_islander = 
          factor(ifelse(is.na(race_pac_islander), "", "pac_islander ")),
        race_white = 
          factor(ifelse(is.na(race_white), "", "white ")),
        race_other_prefno = 
          factor(ifelse(is.na(race_other_prefno), "", "other_prefno ")),
        race_cat = paste0(race_asian_east, race_asian_south, race_asian_other,
                          race_black, race_hispanic, race_middle_eastern,
                          race_native_american, race_pac_islander, race_white,
                          race_other_prefno),
        race_cat2 = factor(sub(" +$", "", race_cat)),
        race_cat3 = factor(ifelse(grepl(" ", race_cat2) == T, "multiracial",
                                  as.character(race_cat2)))) %>%
      select(study, subid:end_time, duration, finished:gender, 
             education:age_approx, race_cat3) %>%
      rename(race_cat = race_cat3)
    
    # filter conditions if desired
    if(is.element("none", chosenExclude)) {} else {
      d_clean <- d_clean %>%
        filter(!condition %in% chosenExclude)
    }
    
    # remove extraneous dfs and variables
    rm(d, d_clean_1, d_clean_2)
  }
  
#   # transform to 0 to 6 scale
#   d_clean <- d_clean %>%
#     gather(mc, score, happy:pride) %>%
#     mutate(score = score + 3) %>% # transform from -3 to 3 --> 0 to 6
#     spread(mc, score)
  
  # remove outliers
  if(chosenOutlierHandling == "remove") {
    
    if(datasource %in% c("study 1", "study 2", "study 4")) {
        d_clean <- d_clean %>%
        gather(mc, score, happy:pride) %>%
        group_by(condition, mc) %>%
        filter(!score %in% boxplot.stats(score, 2.5)$out) %>%
        spread(mc, score) %>%
        arrange(condition, subid)
    }
    
    if(datasource == "study 3") {
      d_clean <- d_clean %>%
        gather(mc, score, happy:pride) %>%
        group_by(target, mc) %>%
        filter(!score %in% boxplot.stats(score, 2.5)$out) %>%
        spread(mc, score) %>%
        arrange(target, subid)
    }
    
  }
  
  # return cleaned dataset
  return(d_clean)
}

# make function for examining exclusion of participants
excludedCounts <- function(datasource) {
  
  # set datasource
  if(datasource == "study 1"){
    d <- d1
    d_raw <- d_raw_study1
  }
  if(datasource == "study 2"){
    d <- d2
    d_raw <- d_raw_study2
  }
  if(datasource == "study 3"){
    d <- d3
    d_raw <- d_raw_study3
  }
  if(datasource == "study 4"){
    d <- d4
    d_raw <- d_raw_study4
  }
  
  # get subids of successful participants
  d_subids <- levels(factor(as.character(d$subid)))
  
  # get subids of excluded participants
  d_excluded <- d_raw %>%
    filter(is.element(subid, d_subids) == FALSE) %>%
    select(condition, subid, finished, starts_with("CATCH"), yob)

  # count excluded participants
  d_excluded_n <- length(d_excluded$subid)
  
  if(datasource %in% c("study 1", "study 2", "study 4")) {
    # count participants who did not finish
    d_excluded_unfinished <- d_excluded %>%
      filter(is.na(CATCH) == T,
             finished != 1) %>%
      select(subid) %>%
      c()
    
    # count participants who finished, but failed catch trial
    d_excluded_CATCH <- d_excluded %>%
      filter(is.element(subid, d_excluded_unfinished$subid) == FALSE) %>%
      filter(CATCH != 1) %>%
      select(subid) %>%
      c()
  }
  
  if(datasource == "study 3") {
    # count participants who did not finish
    d_excluded_unfinished <- d_excluded %>%
      filter(is.na(CATCH..characterL) == T,
             is.na(CATCH..characterR) == T,
             finished != 1) %>%
      select(subid) %>%
      c()
    
    # count participants who finished, but failed catch trial
    d_excluded_CATCH <- d_excluded %>%
      filter(is.element(subid, d_excluded_unfinished$subid) == FALSE) %>%
      filter(CATCH..characterL != 5 | CATCH..characterR != 5) %>%
      select(subid) %>%
      c()
  }
  
  # count participants who finished and passed catch trial, 
  # but did not provide year of birth
  d_excluded_no_yob <- d_excluded %>%
    filter(is.element(subid, d_excluded_unfinished$subid) == FALSE,
           is.element(subid, d_excluded_CATCH$subid) == FALSE) %>%
    mutate(yob = as.numeric(as.character(yob))) %>%
    filter(is.na(yob) | yob < 1899 | nchar(as.character(yob)) != 4) %>%
    select(subid) %>%
    c()
  
  # count participants who finished and passed catch trial, 
  # but did not provide year of birth
  d_excluded_young <- d_excluded %>%
    filter(is.element(subid, d_excluded_unfinished$subid) == FALSE,
           is.element(subid, d_excluded_CATCH$subid) == FALSE,
           is.element(subid, d_excluded_no_yob$subid) == FALSE) %>%
    mutate(yob = as.numeric(as.character(yob))) %>%
    filter(is.na(yob) | 2016 - yob < 18) %>%
    select(subid) %>%
    c()
  
  # sum up excluded participants by category
  total <- sum(length(d_excluded_unfinished$subid),
               length(d_excluded_CATCH$subid),
               length(d_excluded_no_yob$subid),
               length(d_excluded_young$subid))
  
  # calculate counts
  excluded_counts <- 
    data.frame("did_not_finish" = length(d_excluded_unfinished$subid),
               "failed_catch_trial" = length(d_excluded_CATCH$subid),
               "did_not_provide_yob" = length(d_excluded_no_yob$subid),
               "too_young" = length(d_excluded_young$subid),
               "TOTAL_excluded" = total,
               "TOTAL_participated" = length(d$subid),
               "OVERALL_TOTAL" = sum(total, length(d$subid)))
  
  if(total != d_excluded_n) {
    stop("Error: 4 sources of exclusion do not add up to total.")
    } else {
      return(excluded_counts)
    }
}

# make function for stripping dataframes for dimension reducation
makeDRDF <- function(datasource, chosenCondition) {
  
  # set target dataset
  if(datasource == "study 1"){d <- d1}
  if(datasource == "study 2"){d <- d2}
  if(datasource == "study 3"){
    # rename variables for ease of function applpication
    d <- d3 %>%
      rename(order = condition,
             condition = target)
    
    # rename subids by condition if collapses across conditions
    d <- d %>%
      mutate(subid = paste(condition, subid, sep = "_"))
  }
  if(datasource == "study 4"){d <- d4}
  
  # filter by condition if specified
  if(chosenCondition %in% c("beetle", "robot")) {
    d <- d %>% filter(condition == chosenCondition)
  }
  
  # make stripped dataframe for dimension reducation analyses
  d_strip <- d %>%
    select(subid, happy:pride)
  d_strip <- data.frame(d_strip[,-1], row.names = d_strip$subid)
  
  # return stripped dataframe
  return(d_strip)
}

# make demographics functions
demoSampleSize <- function(datasource) {

  # set target dataset
  if(datasource == "study 1"){d <- d1}
  if(datasource == "study 2"){d <- d2}
  if(datasource == "study 3"){
    # rename variables for ease of function applpication
    d <- d3 %>%
      rename(order = condition,
             condition = target)
  }
  if(datasource == "study 4"){d <- d4}

  # get sample size per condition
  sample_size <- vector()
  for(i in levels(d$condition)) {
    sample_size[as.character(i)] <- 
      as.numeric(d %>% filter(condition == i) %>% select(subid) %>% 
                   unique() %>% count())
  }

  # add total sample size  
  sample_size["all"] <- as.numeric(d %>% select(subid) %>% 
                                     unique() %>% count())
  
  # make into dataframe for using kable
  sample_size <- data.frame(sample_size) %>%
    add_rownames() %>%
    rename(condition = rowname,
           n = sample_size)
  
  # return dataframe for using kable
  return(sample_size)
}
demoDuration <- function(datasource) {

  # set target dataset
  if(datasource == "study 1"){d <- d1}
  if(datasource == "study 2"){d <- d2}
  if(datasource == "study 3"){
    # recode variables for ease of function applpication
    d <- d3 %>%
      mutate(condition = "within-subjects")
  }
  if(datasource == "study 4"){d <- d4}

  # get sample size per condition
  duration <- d %>%
    group_by(condition) %>%
    summarise(min_duration = min(duration),
              max_duration = max(duration),
              median_duration = median(duration),
              mean_duration = mean(duration),
              sd_duration = sd(duration))

  # add total duration
  if(datasource %in% c("study 1", "study 2", "study 4")) {
    all <- d %>%
      summarise(min_duration = min(duration),
                max_duration = max(duration),
                median_duration = median(duration),
                mean_duration = mean(duration),
                sd_duration = sd(duration)) %>%
      mutate(condition = "all")
    duration <- rbind(duration, all) # not sure why full_join doesn't work    
  }

  # return dataframe for using kable
  return(duration)
}
demoAge <- function(datasource) {

  # set target dataset
  if(datasource == "study 1"){d <- d1}
  if(datasource == "study 2"){d <- d2}
  if(datasource == "study 3"){
    # recode variables for ease of function applpication
    d <- d3 %>%
      mutate(condition = "within-subjects")
  }
  if(datasource == "study 4"){d <- d4}

  # get sample size per condition
  age <- d %>%
    group_by(condition) %>%
    summarise(min_age = min(age_approx),
              max_age = max(age_approx),
              median_age = median(age_approx),
              mean_age = mean(age_approx),
              sd_age = sd(age_approx))

  # add total age
  if(datasource %in% c("study 1", "study 2", "study 4")) {
    all <- d %>%
      summarise(min_age = min(age_approx),
                max_age = max(age_approx),
                median_age = median(age_approx),
                mean_age = mean(age_approx),
                sd_age = sd(age_approx)) %>%
      mutate(condition = "all")
    age <- full_join(age, all)
  }

  # return dataframe for using kable
  return(age)
}
demoGender <- function(datasource) {

  # set target dataset
  if(datasource == "study 1"){d <- d1}
  if(datasource == "study 2"){d <- d2}
  if(datasource == "study 3"){d <- d3}
  if(datasource == "study 4"){d <- d4}

  # get gender per condition and overall
  if(datasource %in% c("study 1", "study 2", "study 4")) {
    gender <- data.frame(addmargins(with(d, table(condition, gender)))) %>%
      filter(gender != "Sum") %>%
      rename(n = Freq)
  }
  
  if(datasource == "study 3") {
    gender <- data.frame(with(d, table(gender))) %>%
      rename(n = Freq) %>%
      mutate(condition = "Sum") %>%
      select(condition, gender, n)
  }
  
  if(datasource %in% c("study 1", "study 2", "study 3")) {
    gender <- gender %>%
    mutate(condition = factor(ifelse(condition == "Sum", 
                                     "all", as.character(condition)),
                              levels = c("beetle", "robot", "all"))) %>%
    arrange(condition, gender) %>%
    spread(gender, n)
  }
  
  if(datasource == "study 4") {
    gender <- gender %>%
    mutate(condition = factor(ifelse(condition == "Sum", 
                                     "all", as.character(condition)),
                              levels = c(levels(d$condition), "all"))) %>%
    arrange(condition, gender) %>%
    spread(gender, n)
  }
  
  # return dataframe for using kable
  return(gender)
}
demoRace <- function(datasource) {

  # set target dataset
  if(datasource == "study 1"){d <- d1}
  if(datasource == "study 2"){d <- d2}
  if(datasource == "study 3"){d <- d3}
  if(datasource == "study 4"){d <- d4}

  # get race per condition and overall
  if(datasource %in% c("study 1", "study 2", "study 4")) {
    race <- data.frame(addmargins(with(d, table(condition, race_cat)))) %>%
      filter(race_cat != "Sum") %>%
      rename(n = Freq)
  }
  
  if(datasource == "study 3") {
    race <- data.frame(with(d, table(race_cat))) %>%
      rename(n = Freq) %>%
      mutate(condition = "Sum") %>%
      select(condition, race_cat, n)
  }
  
  if(datasource %in% c("study 1", "study 2", "study 3")) {
    race <- race %>%
    mutate(condition = factor(ifelse(condition == "Sum", 
                                     "all", as.character(condition)),
                              levels = c("beetle", "robot", "all"))) %>%
    arrange(condition, race_cat) %>%
    spread(race_cat, n)
  }
  
  if(datasource == "study 4") {
    race <- race %>%
    mutate(condition = factor(ifelse(condition == "Sum", 
                                     "all", as.character(condition)),
                              levels = c(levels(d$condition), "all"))) %>%
    arrange(condition, race_cat) %>%
    spread(race_cat, n)
  }
  
  # return dataframe for using kable
  return(race)
}
demoReligion <- function(datasource) {

  # set target dataset
  if(datasource == "study 1"){d <- d1}
  if(datasource == "study 2"){d <- d2}
  if(datasource == "study 3"){d <- d3}

  # get religion per condition and overall
  if(datasource %in% c("study 1", "study 2")) {
    religion <- data.frame(addmargins(with(d, table(condition, religion_cat)))) %>%
      filter(religion_cat != "Sum") %>%
      rename(n = Freq)
  }
  
  if(datasource == "study 3") {
    religion <- data.frame(with(d, table(religion_cat))) %>%
      rename(n = Freq) %>%
      mutate(condition = "Sum") %>%
      select(condition, religion_cat, n)
  }
  
  if(datasource %in% c("study 1", "study 2", "study 3")) {
    religion <- religion %>%
    mutate(condition = factor(ifelse(condition == "Sum", 
                                     "all", as.character(condition)),
                              levels = c("beetle", "robot", "all"))) %>%
    arrange(condition, religion_cat) %>%
    spread(religion_cat, n)
  }
  
  # return dataframe for using kable
  if(datasource == "study 4"){
    stop("Religion information not available for Study 4")
  } else {return(religion)}
}
demoEducation <- function(datasource) {

  # set target dataset
  if(datasource == "study 4"){d <- d4}
  
  # get education per condition and overall
  if(datasource == "study 4") {
    education <- 
      data.frame(addmargins(with(d, table(condition, education)))) %>%
      filter(education != "Sum") %>%
      rename(n = Freq) %>%
      mutate(condition = factor(ifelse(condition == "Sum",
                                       "all", as.character(condition)),
                                levels = c(levels(d$condition), "all")),
             education = factor(education,
                                levels = c(1:7, 0),
                                labels = c("some_HS",
                                           "HS_diploma",
                                           "some_college",
                                           "associates",
                                           "bachelors",
                                           "some_grad",
                                           "grad",
                                           "pref_no"))) %>%
      arrange(condition, education) %>%
      spread(education, n)
  }
  
  # return dataframe for using kable
  if(datasource %in% c("study 1", "study 2", "study 3")){
    stop("Education information not available for Studies 1-3")
  } else {return(education)}
}

# set 21-color palette (thank to Paul Tol: https://personal.sron.nl/~pault/colourschemes.pdf)
tol21rainbow = c("#771155", "#AA4488", "#CC99BB", "#114477", "#4477AA", "#77AADD", "#117777", "#44AAAA", "#77CCCC", "#117744", "#44AA77", "#88CCAA", "#777711", "#AAAA44", "#DDDD77", "#774411", "#AA7744", "#DDAA77", "#771122", "#AA4455", "#DD7788")
```

```{r modeling decisions, echo = F}
# remove outliers?
chosenOutlierHandling <- "keep"
# chosenOutlierHandling <- "remove"

# exclude any conditions in study 4?
chosenExclude <- "none"
# chosenExclude <- c("stapler", "car", "computer")

# for current purposes always choose minimal residual (fm = "minres") instead of ML because of non-normality

# for EFAs, what kind of correlation?
chosenCorType <- "cor" # pearson correlation, less appropriate for ordinal data but 7-point likert scale might be ok
# chosenCorType <- "poly" # polychoric correlation, appropriate for ordinal data but seems to throw errors

kable(data.frame("conditionsExcluded" = chosenExclude,
                 "outlierHandling" = chosenOutlierHandling, 
                 "EFA_correlation" = chosenCorType))
```

<p style="text-align:right"><a href="#header">back to TOC</a></p>

# Data preparation

```{r data upload, message = F, echo = F}
# study 1 (2015-12-15, 2 conditions, between-subjects)
d_raw_study1 <- read.csv("/Users/kweisman/Documents/Research (Stanford)/Projects/GGW-mod/ggw-mod2/mturk/v1 (2 conditions between)/GGWmod2_v1_clean.csv") %>%
  mutate(study = "study 1")

# study 2 (2016-01-12, 2 conditions, between-subjects - REPLICATION)
d_raw_study2 <- read.csv("/Users/kweisman/Documents/Research (Stanford)/Projects/GGW-mod/ggw-mod2/mturk/v1 (replication)/GGWmod2_v1_replication_clean.csv") %>%
  mutate(study = "study 2")

# study 3 (2016-01-10, 2 conditions, within-subjects)
d_raw_study3 <- read.csv("/Users/kweisman/Documents/Research (Stanford)/Projects/GGW-mod/ggw-mod2/mturk/v2 (2 conditions within)/GGWmod2_v2_withinsubjects_clean.csv") %>%
  mutate(study = "study 3")

# study 4 (2016-01-14, 21 conditions, between-subjects)
d_raw_study4 <- read.csv("/Users/kweisman/Documents/Research (Stanford)/Projects/GGW-mod/ggw-mod2/mturk/v3 (21 conditions between)/GGWmod2_v3_many_characters_clean.csv") %>%
  mutate(study = "study 4")
```

```{r data cleanup, message = F, echo = F}
# clean up datasets
d1 <- cleanup("study 1")
d2 <- cleanup("study 2")
d3 <- cleanup("study 3")
d4 <- cleanup("study 4")
```

```{r dataframes for dimension reducation, message = F, echo = F}
# make dataframes for s1
d1_beetle <- makeDRDF("study 1", "beetle")
d1_robot <- makeDRDF("study 1", "robot")
d1_all <- makeDRDF("study 1", "all")

# make dataframes for study 2
d2_beetle <- makeDRDF("study 2", "beetle")
d2_robot <- makeDRDF("study 2", "robot")
d2_all <- makeDRDF("study 2", "all")

# make dataframes for study 3
d3_beetle <- makeDRDF("study 3", "beetle")
d3_robot <- makeDRDF("study 3", "robot")
d3_all <- makeDRDF("study 3", "all")

# make dataframes for study 4
d4_all <- makeDRDF("study 4", "all")
```

<p style="text-align:right"><a href="#header">back to TOC</a></p>

# Study 1 (2015-12-15, 2 conditions, between-subjects)

## Demographics

```{r s1 demographics, echo = F}
# examine exclusion
kable(excludedCounts("study 1"), align = "l",
      caption = "Study 1: Exclusion")

# make demographics tables
kable(demoSampleSize("study 1"), align = "l", digits = 2,
      caption = "Study 1: Sample size")
kable(demoDuration("study 1"), align = "l", digits = 2,
      caption = "Study 1: Study duration (minutes)")
kable(demoAge("study 1"), align = "l", digits = 2,
      caption = "Study 1: Participant age (years; approximate)")
kable(demoGender("study 1"), align = "l", digits = 2,
      caption = "Study 1: Participant gender")
kable(demoRace("study 1"), align = "l", digits = 2,
      caption = "Study 1: Participant race/ethnicity")
kable(demoReligion("study 1"), align = "l", digits = 2,
      caption = "Study 1: Participant religion")
```

<p style="text-align:right"><a href="#header">back to TOC</a></p>

## Exploratory factor analysis

### Step 1: Run EFA without rotation

```{r s1 all no rotation, echo = F}
# examine scree plot
scree(d1_all)

# run EFA without rotation with N factors
efa_d1_all_unrotated <- fa(d1_all, 39, rotate = "none",
                           cor = chosenCorType, fm = "minres")
print(efa_d1_all_unrotated)

# set number of factors to extract: eigenvalue > 1, variance explained > 5%
nfactors_d1_all <- 3
```

### Step 3: Run EFA with varimax rotation

```{r s1 all varimax rotation, echo = F}
# run EFA with rotation with N factors
efa_d1_all_rotatedN <- fa(d1_all, nfactors_d1_all, 
                          rotate = "varimax", cor = chosenCorType, fm = "minres")
print(efa_d1_all_rotatedN)

# get loadings for each factor
efa_d1_all_rotatedN_loadings <- loadings(efa_d1_all_rotatedN)[] %>%
  data.frame() %>% 
  add_rownames(var = "mc")
```

<p style="text-align:right"><a href="#header">back to TOC</a></p>

#### Factor 1

```{r s1 all varimax rotation F1, echo = F}
# examine factor 1
kable(efa_d1_all_rotatedN_loadings %>% select(mc, MR1) %>% arrange(desc(MR1)),
      align = "l", caption = "Study 1, ALL conditions: Rotated Factor 1")
```

#### Factor 2

```{r s1 all varimax rotation F2, echo = F}
# examine factor 1
kable(efa_d1_all_rotatedN_loadings %>% select(mc, MR2) %>% arrange(desc(MR2)),
      align = "l", caption = "Study 1, ALL conditions: Rotated Factor 2")
```

#### Factor 3

```{r s1 all varimax rotation F3, echo = F}
# examine factor 1
kable(efa_d1_all_rotatedN_loadings %>% select(mc, MR3) %>% arrange(desc(MR3)),
      align = "l", caption = "Study 1, ALL conditions: Rotated Factor 3")
```

#### Factor loadings table

```{r s1 loadings table, echo = F}
kable(data.frame(loadings(fa.sort(efa_d1_all_rotatedN))[]), digits = 2)
```

# Study 2 (2016-01-12, 2 conditions, between-subjects - REPLICATION)

## Demographics

```{r s2 demographics, echo = F}
# examine exclusion
kable(excludedCounts("study 2"), align = "l",
      caption = "Study 2: Exclusion")

# make demographics tables
kable(demoSampleSize("study 2"), align = "l", digits = 2,
      caption = "Study 2: Sample size")
kable(demoDuration("study 2"), align = "l", digits = 2,
      caption = "Study 2: Study duration (minutes)")
kable(demoAge("study 2"), align = "l", digits = 2,
      caption = "Study 2: Participant age (years; approximate)")
kable(demoGender("study 2"), align = "l", digits = 2,
      caption = "Study 2: Participant gender")
kable(demoRace("study 2"), align = "l", digits = 2,
      caption = "Study 2: Participant race/ethnicity")
kable(demoReligion("study 2"), align = "l", digits = 2,
      caption = "Study 2: Participant religion")
```

<p style="text-align:right"><a href="#header">back to TOC</a></p>

## Exploratory factor analysis

### Step 1: Run EFA without rotation

```{r s2 all no rotation, echo = F}
# examine scree plot
scree(d2_all)

# run EFA without rotation with N factors
efa_d2_all_unrotated <- fa(d2_all, 39, rotate = "none",
                           cor = chosenCorType, fm = "minres")
print(efa_d2_all_unrotated)

# set number of factors to extract: eigenvalue > 1, variance explained > 5%
nfactors_d2_all <- 3
```

### Step 3: Run EFA with varimax rotation

```{r s2 all varimax rotation, echo = F}
# run EFA with rotation with N factors
efa_d2_all_rotatedN <- fa(d2_all, nfactors_d2_all, 
                          rotate = "varimax", cor = chosenCorType, fm = "minres")
print(efa_d2_all_rotatedN)

# get loadings for each factor
efa_d2_all_rotatedN_loadings <- loadings(efa_d2_all_rotatedN)[] %>%
  data.frame() %>% 
  add_rownames(var = "mc")
```

<p style="text-align:right"><a href="#header">back to TOC</a></p>

#### Factor 1

```{r s2 all varimax rotation F1, echo = F}
# examine factor 1
kable(efa_d2_all_rotatedN_loadings %>% select(mc, MR1) %>% arrange(desc(MR1)),
      align = "l", caption = "Study 2, ALL conditions: Rotated Factor 1")
```

#### Factor 2

```{r s2 all varimax rotation F2, echo = F}
# examine factor 1
kable(efa_d2_all_rotatedN_loadings %>% select(mc, MR2) %>% arrange(desc(MR2)),
      align = "l", caption = "Study 2, ALL conditions: Rotated Factor 2")
```

#### Factor 3

```{r s2 all varimax rotation F3, echo = F}
# examine factor 1
kable(efa_d2_all_rotatedN_loadings %>% select(mc, MR3) %>% arrange(desc(MR3)),
      align = "l", caption = "Study 2, ALL conditions: Rotated Factor 3")
```

#### Factor loadings table

```{r s2 loadings table, echo = F}
kable(data.frame(loadings(fa.sort(efa_d2_all_rotatedN))[]), digits = 2)
```

# Study 3 (2016-01-10, 2 conditions, within-subjects)

## Demographics

```{r s3 demographics, echo = F}
# examine exclusion
kable(excludedCounts("study 3"), align = "l",
      caption = "Study 3: Exclusion")

# make demographics tables
kable(demoSampleSize("study 3"), align = "l", digits = 2,
      caption = "Study 3: Sample size")
kable(demoDuration("study 3"), align = "l", digits = 2,
      caption = "Study 3: Study duration (minutes)")
kable(demoAge("study 3"), align = "l", digits = 2,
      caption = "Study 3: Participant age (years; approximate)")
kable(demoGender("study 3"), align = "l", digits = 2,
      caption = "Study 3: Participant gender")
kable(demoRace("study 3"), align = "l", digits = 2,
      caption = "Study 3: Participant race/ethnicity")
kable(demoReligion("study 3"), align = "l", digits = 2,
      caption = "Study 3: Participant religion")
```

<p style="text-align:right"><a href="#header">back to TOC</a></p>

## Exploratory factor analysis

### Step 1: Run EFA without rotation

```{r s3 all no rotation, echo = F}
# examine scree plot
scree(d3_all)

# run EFA without rotation with N factors
efa_d3_all_unrotated <- fa(d3_all, 39, rotate = "none",
                           cor = chosenCorType, fm = "minres")
print(efa_d3_all_unrotated)

# set number of factors to extract: eigenvalue > 1, variance explained > 5%
nfactors_d3_all <- 3
```

### Step 3: Run EFA with varimax rotation

```{r s3 all varimax rotation, echo = F}
# run EFA with rotation with N factors
efa_d3_all_rotatedN <- fa(d3_all, nfactors_d3_all, 
                          rotate = "varimax", cor = chosenCorType, fm = "minres")
print(efa_d3_all_rotatedN)

# get loadings for each factor
efa_d3_all_rotatedN_loadings <- loadings(efa_d3_all_rotatedN)[] %>%
  data.frame() %>% 
  add_rownames(var = "mc")
```

<p style="text-align:right"><a href="#header">back to TOC</a></p>

#### Factor 1

```{r s3 all varimax rotation F1, echo = F}
# examine factor 1
kable(efa_d3_all_rotatedN_loadings %>% select(mc, MR1) %>% arrange(desc(MR1)),
      align = "l", caption = "Study 3, ALL conditions: Rotated Factor 1")
```

#### Factor 2

```{r s3 all varimax rotation F2, echo = F}
# examine factor 1
kable(efa_d3_all_rotatedN_loadings %>% select(mc, MR2) %>% arrange(desc(MR2)),
      align = "l", caption = "Study 3, ALL conditions: Rotated Factor 2")
```

#### Factor 3

```{r s3 all varimax rotation F3, echo = F}
# examine factor 1
kable(efa_d3_all_rotatedN_loadings %>% select(mc, MR3) %>% arrange(desc(MR3)),
      align = "l", caption = "Study 3, ALL conditions: Rotated Factor 3")
```

#### Factor loadings table

```{r s3 loadings table, echo = F}
kable(data.frame(loadings(fa.sort(efa_d3_all_rotatedN))[]), digits = 2)
```

# Study 4 (2016-01-14, 21 conditions, between-subjects)

## Demographics

```{r s4 demographics, echo = F}
# examine exclusion
kable(excludedCounts("study 4"), align = "l",
      caption = "Study 4: Exclusion")

# make demographics tables
kable(demoSampleSize("study 4"), align = "l", digits = 2,
      caption = "Study 4: Sample size")
kable(demoDuration("study 4"), align = "l", digits = 2,
      caption = "Study 4: Study duration (minutes)")
kable(demoAge("study 4"), align = "l", digits = 2,
      caption = "Study 4: Participant age (years; approximate)")
kable(demoGender("study 4"), align = "l", digits = 2,
      caption = "Study 4: Participant gender")
kable(demoRace("study 4"), align = "l", digits = 2,
      caption = "Study 4: Participant race/ethnicity")
kable(demoEducation("study 4"), align = "l", digits = 2,
      caption = "Study 4: Participant education")
```

<p style="text-align:right"><a href="#header">back to TOC</a></p>

## Exploratory factor analysis

### Step 1: Run EFA without rotation

```{r s4 all no rotation, echo = F}
# examine scree plot
scree(d4_all)

# run EFA without rotation with N factors
efa_d4_all_unrotated <- fa(d4_all, 39, rotate = "none",
                           cor = chosenCorType, fm = "minres")
print(efa_d4_all_unrotated)

# set number of factors to extract: eigenvalue > 1, variance explained > 5%
nfactors_d4_all <- 3
```

### Step 3: Run EFA with varimax rotation

```{r s4 all varimax rotation, echo = F}
# run EFA with rotation with N factors
efa_d4_all_rotatedN <- fa(d4_all, nfactors_d4_all, 
                          rotate = "varimax", cor = chosenCorType, fm = "minres")
print(efa_d4_all_rotatedN)

# get loadings for each factor
efa_d4_all_rotatedN_loadings <- loadings(efa_d4_all_rotatedN)[] %>%
  data.frame() %>% 
  add_rownames(var = "mc")
```

<p style="text-align:right"><a href="#header">back to TOC</a></p>

#### Factor 1

```{r s4 all varimax rotation F1, echo = F}
# examine factor 1
kable(efa_d4_all_rotatedN_loadings %>% select(mc, MR1) %>% arrange(desc(MR1)),
      align = "l", caption = "Study 4, ALL conditions: Rotated Factor 1")
```

#### Factor 2

```{r s4 all varimax rotation F2, echo = F}
# examine factor 1
kable(efa_d4_all_rotatedN_loadings %>% select(mc, MR2) %>% arrange(desc(MR2)),
      align = "l", caption = "Study 4, ALL conditions: Rotated Factor 2")
```

#### Factor 3

```{r s4 all varimax rotation F3, echo = F}
# examine factor 1
kable(efa_d4_all_rotatedN_loadings %>% select(mc, MR3) %>% arrange(desc(MR3)),
      align = "l", caption = "Study 4, ALL conditions: Rotated Factor 3")
```

#### Factor loadings table

```{r s4 loadings table, echo = F}
kable(data.frame(loadings(fa.sort(efa_d4_all_rotatedN))[]), digits = 2)
```

#### Plots! 

```{r s4 efa plotting df, echo = F}
# make dataframe for plotting
efa_d4_all_rotatedN_scores <- efa_d4_all_rotatedN$scores %>%
  data.frame() %>%
  add_rownames(var = "subid") %>%
  full_join(d4 %>% select(subid, condition)) %>%
  select(condition, subid, MR1, MR2, MR3) # %>%
#   mutate(MR1_rescale = scales::rescale(MR1, to = c(0, 1)),
#          MR2_rescale = scales::rescale(MR2, to = c(0, 1)),
#          MR3_rescale = scales::rescale(MR3, to = c(0, 1)))

efa_d4_all_rotatedN_scores_F1 <- efa_d4_all_rotatedN_scores %>%
  multi_boot(column = "MR1",
             summary_groups = "condition",
             summary_function = "mean_na",
             statistics_functions = c("ci_lower_na", "mean_na", "ci_upper_na")) %>%
  rename(F1_ci_lower = ci_lower_na, F1_mean = mean_na, F1_ci_upper = ci_upper_na)

efa_d4_all_rotatedN_scores_F2 <- efa_d4_all_rotatedN_scores %>%
  multi_boot(column = "MR2",
             summary_groups = "condition",
             summary_function = "mean_na",
             statistics_functions = c("ci_lower_na", "mean_na", "ci_upper_na")) %>%
  rename(F2_ci_lower = ci_lower_na, F2_mean = mean_na, F2_ci_upper = ci_upper_na)

efa_d4_all_rotatedN_scores_F3 <- efa_d4_all_rotatedN_scores %>%
  multi_boot(column = "MR3",
             summary_groups = "condition",
             summary_function = "mean_na",
             statistics_functions = c("ci_lower_na", "mean_na", "ci_upper_na")) %>%
  rename(F3_ci_lower = ci_lower_na, F3_mean = mean_na, F3_ci_upper = ci_upper_na)

efa_d4_all_rotatedN_scores <- efa_d4_all_rotatedN_scores_F1 %>%
  full_join(efa_d4_all_rotatedN_scores_F2) %>%
  full_join(efa_d4_all_rotatedN_scores_F3)

# remove extraneous variables
rm(efa_d4_all_rotatedN_scores_F1, efa_d4_all_rotatedN_scores_F2, 
   efa_d4_all_rotatedN_scores_F3)
```

```{r s4 efa plot F1 vs F2, echo = F, fig.width = 8, fig.height = 8}
d4_f1f2 <- ggplot(aes(x = F1_mean, y = F2_mean, 
                      label = condition, colour = condition),
                  data = efa_d4_all_rotatedN_scores) +
  geom_errorbar(aes(ymin = F2_ci_lower, ymax = F2_ci_upper), 
                width = 0.01, alpha = 0.3) +
  geom_errorbarh(aes(xmin = F1_ci_lower, xmax = F1_ci_upper),
                 height = 0.01, alpha = 0.3) +
  geom_point(size = 4) +
  geom_dl(aes(label = condition), method = "smart.grid") +
  # geom_text(aes(y = F2_mean + 0.05)) +
  theme_bw() +
  scale_color_manual(values = tol21rainbow) +
#   scale_x_continuous(name = "Factor 1",
#                      limits = c(0, 1),
#                      breaks = c(0, 1)) +
#   scale_y_continuous(name = "Factor 2",
#                      limits = c(0, 1),
#                      breaks = c(0, 1)) +
  theme(text = element_text(size = 20),
        legend.position = "none") +
  labs(title = "Study 3: Average factor scores\n")
```

```{r s4 efa plot F1 vs F3, echo = F, fig.width = 8, fig.height = 8}
d4_f1f3 <- ggplot(aes(x = F1_mean, y = F3_mean, 
                      label = condition, colour = condition),
                  data = efa_d4_all_rotatedN_scores) +
  geom_errorbar(aes(ymin = F3_ci_lower, ymax = F3_ci_upper), 
                width = 0.01, alpha = 0.3) +
  geom_errorbarh(aes(xmin = F1_ci_lower, xmax = F1_ci_upper),
                 height = 0.01, alpha = 0.3) +
  geom_point(size = 4) +
  geom_dl(aes(label = condition), method = "smart.grid") +
  # geom_text(aes(y = F3_mean + 0.05)) +
  theme_bw() +
  scale_color_manual(values = tol21rainbow) +
#   scale_x_continuous(name = "Factor 1",
#                      limits = c(0, 1),
#                      breaks = c(0, 1)) +
#   scale_y_continuous(name = "Factor 3",
#                      limits = c(0, 1),
#                      breaks = c(0, 1)) +
  theme(text = element_text(size = 20),
        legend.position = "none") +
  labs(title = "")
```

```{r s4 efa plot F2 vs F3, echo = F, fig.width = 8, fig.height = 8}
d4_f2f3 <- ggplot(aes(x = F2_mean, y = F3_mean, 
                      label = condition, colour = condition),
                  data = efa_d4_all_rotatedN_scores) +
  geom_errorbar(aes(ymin = F3_ci_lower, ymax = F3_ci_upper), 
                width = 0.01, alpha = 0.3) +
  geom_errorbarh(aes(xmin = F2_ci_lower, xmax = F2_ci_upper),
                 height = 0.01, alpha = 0.3) +
  geom_point(size = 4) +
  geom_dl(aes(label = condition), method = "smart.grid") +
  # geom_text(aes(y = F3_mean + 0.05)) +
  theme_bw() +
  scale_color_manual(values = tol21rainbow) +
#   scale_x_continuous(name = "Factor 2",
#                      limits = c(0, 1),
#                      breaks = c(0, 1)) +
#   scale_y_continuous(name = "Factor 3",
#                      limits = c(0, 1),
#                      breaks = c(0, 1)) +
  theme(text = element_text(size = 20),
        legend.position = "none") +
    labs(title = "")
```

```{r s4 plots, fig.width = 8, fig.height = 20}
grid.arrange(d4_f1f2, d4_f1f3, d4_f2f3, ncol = 1)
```

# Big factor loadings table

```{r all studies loadings table, echo = F}
order1 <- loadings(fa.sort(efa_d1_all_rotatedN))[] %>%
  data.frame() %>%
  add_rownames(var = "mc") %>%
  add_rownames(var = "order1") %>%
  rename(s1_MR2 = MR2, s1_MR1 = MR1, s1_MR3 = MR3)

s2 <- loadings(fa.sort(efa_d2_all_rotatedN))[] %>%
  data.frame() %>%
  add_rownames(var = "mc") %>%
  rename(s2_MR2 = MR2, s2_MR1 = MR1, s2_MR3 = MR3)

s3 <- loadings(fa.sort(efa_d3_all_rotatedN))[] %>%
  data.frame() %>%
  add_rownames(var = "mc") %>%
  rename(s3_MR2 = MR2, s3_MR1 = MR1, s3_MR3 = MR3)

s4 <- loadings(fa.sort(efa_d4_all_rotatedN))[] %>%
  data.frame() %>%
  add_rownames(var = "mc") %>%
  rename(s4_MR2 = MR2, s4_MR1 = MR1, s4_MR3 = MR3)

bigTable <- order1 %>%
  # full_join(s2) %>%
  full_join(s3) %>%
  full_join(s4)

# remove extraneous variables
rm(s1, s2, s3, s4)

kable(bigTable, digits = 2)
```


